---
title: "Reproducible Reporting"
author: "Edward Bosko"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(kableExtra)
```

## Reproducible Reporting

```{r}
dat <- read.csv('C:/Users/Eddie/OneDrive/Desktop/BIOSTAT/BIOS 6621/Week 6/lead-iq-01.csv')
outlier <- which(dat$IQ==999)
dat$IQ[outlier] <- 99
```

### Make graph

```{r}
boxplot(IQ ~ Smelter, data = dat, main = 'IQ by Distance from Smelter', ylab = 'IQ')
```

### Make table

```{r}
mymod <- lm(IQ ~ as.factor(Smelter), data = dat)
summary(mymod)

df <- data.frame(
  estimate = c(92.687, -3.494),
  SE = c(1.754, 2.587),
  teststat <- c(52.847, -1.351),
  pval <- c('<0.0001', '0.179')
)
colnames(df) = c('Estimate', 'SE','Test Statistic', 'P-Value')

df %>% kable(caption = "Model Output of mymod")
```

We clearly see from our boxplot that the outlier is gone. From our simple linear regression model, we see that children who are within 1 mile of the smelter are expected to have an IQ 3.494 points fewer when compared to children who live further than 1 mile from the smelter, although this difference is not statistically significant (p=0.179).

```{r}
mean(dat$IQ)
```